Bounds on the dimension of consistent convex surrogates

### 2020-05-25 neurips-20/cvx-flats.tex
Added proof that FSD stays the same

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, we have $\dim(\S_{\gamma_r}(p)) = \dim(\S'_{\gamma_r}(p))$, where $\S_{\gamma_r}(p) := \S_{\gamma_r}(p) \cap \spn(\{e_y : y \in \supp(p) \}$.
\end{lemma}
\begin{proof}
	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	\begin{align*}
	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
	\end{align*}
	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		\jessie{This is where I'm stuck??}

>>>>

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, we have $\dim(\S_{\gamma_r}(p)) = \dim(\S'_{\gamma_r}(p))$, where $\S_{\gamma_r}(p) := \S_{\gamma_r}(p) \cap \spn(\{e_y : y \in \supp(p) \}$.
\end{lemma}
\begin{proof}
	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	\begin{align*}
	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
	\end{align*}
	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.

	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}
